Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
pass on 8.1

\begin{figure}[t]
%  \vspace{-2ex}
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 150 0 180,clip,width=\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 150 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}
  }
  \caption{\label{fig:summary}Summary of bug reports.}
  \vspace{-3ex}
\end{figure}

@@

We issued several bug reports as result of this work. For space, we
are unable to discuss all of them. We sampled some bug reports to
discuss in the following. The selection criteria we used was: (i) to
cover all engines we found bugs--\chakra, \jsc, and \veight, (ii) to
cover each technique--test transplantation and differential testing
(with \radamsa\ and with \quickfuzz), (iii) to cover a case of
rejected bug report, and (iv) to use short tests (for space).

@@

@@

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}  The
code {\footnotesize\ttfamily{eval(function b(a)\{break;\});}} shows
the test input we used to reveal a bug in \veight{}. This code snippet
was obtained by fuzzing a Test262 test with \quickfuzz. In its
original version, a string (omitted for space), passed as argument to
the \CodeIn{eval} function, encoded the actual test. The fuzzer
replaced the string argument with a function whose body is a
\CodeIn{break} statement outside a valid block statement. Section
B.3.3.3 from the spec~\cite{spec-b333} documents how eval should
handle code containing function declarations.  According to the
spec~\cite{break-statement}, the virtual machine should throw an early
error--in this case, a SyntaxError--if the break statement is not
nested in an iterable or a switch statement. All engines, but
\veight{}, behave as expected in this case.

\vspace{1ex}\noindent\textbf{Issue \#18,
  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
shows the test input we used to reveal a bug in \jsc. This test
originates from \jerry{} test suite; the bug was found during the test
transplantation experiment.

@@

According to the specification~\cite{ecmas262-array-sort}, the
parameter to the \CodeIn{Array.sort} function should be a comparable
object or an undefined value, otherwise it should throw a
\CodeIn{TypeError}. In this case, \jsc accepts a non-callable object
as argument to \CodeIn{sort} and the test fails in the subsequent
step. The other engines raise a \CodeIn{TypeError} as expected.

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
code snippet below shows an example input related to a bug report that
we issued to the \chakra\ development team, but they did not accept.

@@

This is a test case original from the \jsc suite that the
\radamsa\ fuzzer modified. The original test used the integer literal
3 as argument to \CodeIn{repeat()}, but this test uses a long integer
instead. As result, the engine crashes. The team answered that this
was an incompatibility by design as the function was not expected to
receive such a long value.

>>>>

\begin{figure}[t]
%  \vspace{-2ex}
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 150 0 180,clip,width=\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bug reports per technique.]{
    \includegraphics[trim=0 150 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}
  }
  \caption{\label{fig:summary}Summary of bug reports.}
  \vspace{-3ex}
\end{figure}

@@

We issued several bug reports as result of this work. For space, we
are unable to discuss all of them. We sampled some bug reports to
discuss in the following. The selection criteria we used was:
\begin{enumerate}
\item to cover all engines we found bugs--\chakra, \hermes, \jsc,
  \smonkey, \veight (see Figure~\ref{fig:summary});
\item to cover each technique--test transplantation and differential
  testing;
\item to cover a case of rejected bug report;
\item to use short tests (for space).  
\end{enumerate}

@@

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.} The
snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
revealed a bug in \veight{} version 7.0.244. This code snippet was
obtained by fuzzing a Test262 test with \quickfuzz. In its original
version, a string (omitted for space), passed as argument to the
\CodeIn{eval} function, encoded the actual test. The fuzzer replaced
the string argument with a function whose body is a \CodeIn{break}
statement outside a valid block statement. Section B.3.3.3 from the
\es\ spec~\cite{spec-b333} documents how eval should handle code
containing function declarations.  According to the
spec~\cite{break-statement}, the virtual machine should throw an early
error--in this case, a SyntaxError--if the break statement is not
nested in a loop or switch statement. All engines, but \veight{},
behave as expected in this case.

@@

\vspace{1ex}\noindent\textbf{Issue \#18,
  Table~\ref{tab:test-transplantation-bugs}.}\Mar{$\leftarrow$ isto
  esta errado! A tabela diz que eh Chakra}  The code snippet below
shows the test input we used to reveal a bug in \jsc.

@@

This is a test case of the \jerry{} suite. The bug was found during
the test transplantation experiment. According to the
\es\ spec~\cite{ecmas262-array-sort}, the parameter to the
\CodeIn{Array.sort} function should be a comparable object or an
undefined value, otherwise it should throw a \CodeIn{TypeError}. In
this case, \jsc incorrectly accepts a non-callable object as argument
to \CodeIn{sort} and the test fails in the subsequent step. The other
engines raise a \CodeIn{TypeError} as expected.

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.} We
reported the code snippet below to the \chakra\ development team as a
bug, but they did \emph{not} accept.

@@

This is a test case original from the \jsc suite that the
\radamsa\ fuzzer modified. The original test used the integer literal
3 as argument to \CodeIn{repeat()}, \ie{}, the expression produced a
string with three repetitiong of the string ``foo''. The new test uses
a long integer instead as parameter to \CodeIn{repeat()}. As result,
the engine crashes. The team answered that this was an incompatibility
by design\footnote{We interpreted as a violation of an undocumented
  precondition} as the function was not expected to receive such a
long value.
